---
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse=TRUE, comment="##", fig.retina=2, fig.path = "figures/plot-")
```

# Breaking Down BTS

As a k-pop fan since 2008, I've always been curious and amused with the English words interspersed amongst the Korean lyrics. Do they always make sense? _No._ But are they catchy? _Yes._ 

I started my descriptive analysis with the current most popular K-Pop boy band: BTS. I scraped all the lyrics from [here](https://colorcodedlyrics.com/2014/01/bts-lyrics-index) (though I did try the Genius R Package and AZ Lyrics, I ended up picking ColorCodedLyrics for its simpler HTML format which helped a great deal when parsing it into XML). With the guidance of [Text Mining with R](https://www.tidytextmining.com/), I learned how to tokenize each word, filter out the English words, and make beautiful graphs with them. I also used the helper functions for rvest from [here](https://github.com/tidyverse/rvest/issues/175#issuecomment-266434812) to deal with parsing `<BR>` tags. 


``` {r message=F, warning=F, echo=F, eval=T}
library(magrittr)
library(dplyr)
library(tibble)
library(tidytext)
library(ggplot2)
library(scales)
library(tidyr)
library(readr)

bts_songs_df <- read_csv("data/raw_data/raw_BTS_songs.csv")
tidy_bts_songs_df <- read_csv("data/tidy_data/tidy_BTS_songs.csv")
```


The raw data scraped from Color Coded Lyrics:

``` {r message=F, warning=F, echo=T, eval=T}
bts_songs_df
```



There were 47 total duplicate songs amongst the 6 albums and I removed them because I wanted to analyze English lyrics from _unique_ songs. The data after tidying and finding each individual lyric:

``` {r message=F, warning=F, echo=T, eval=T}
tidy_bts_songs_df
```


``` {r message=FALSE, warning=FALSE, echo=FALSE, eval=TRUE}


tidy_bts_songs_df <- read_csv("data/tidy_data/tidy_BTS_songs.csv")

tidy_bts_songs_freq <- tidy_bts_songs_df %>%
  filter(eng==1) %>%
  count(album_title, word) %>%
  group_by(album_title) %>%
  mutate(proportion = n/sum(n))

tidy_bts_songs_meaningful <- tidy_bts_songs_df %>%
  filter(eng==1) %>%
  anti_join(stop_words)


tidy_bts_songs_meaningful_freq <- tidy_bts_songs_meaningful %>%
  filter(eng==1) %>%
  count(album_title, word) %>%
  group_by(album_title) %>%
  mutate(proportion = n/sum(n))

```


These are literally **_all_** the English words in all of their albums. Some of the words are debatable in terms of whether they're meaningful English words like _oh_ or _ay_. 

``` {r lyrics, message=FALSE, warning=FALSE, echo=FALSE, eval=TRUE, fig.height=9.5, fig.width=9.5}

tidy_bts_songs_freq %>%
  ggplot(aes(x = proportion, y = proportion)) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 0.5) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(aes(color="FE769C"), alpha = 0.2, size = 2.5, width = 0.6, height = 0.6,
              show.legend = F) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  ggtitle("All English Words in All BTS's Albums")
```



I used the dataset `stop_words` from tidytext and added extra words to that dataset to remove common words that aren't as interesting for this analysis:

``` {r message=FALSE, warning=FALSE, echo=FALSE, eval=TRUE}

custom_stop_words <- bind_rows(tibble(word = c("ay", "ayy", "la", "i'm", "uh",
                                               "i'll", "yeah", "hey", "ap"),
                                      lexicon = c("custom")),
                               stop_words)


tidy_bts_songs_meaningful_freq <- tidy_bts_songs_meaningful %>%
  filter(eng==1) %>%
  mutate(word = gsub("\u2019", "'", word)) %>%
  anti_join(custom_stop_words) %>%
  count(album_title, word) %>%
  group_by(album_title) %>%
  mutate(proportion = n/sum(n))

```
``` {r meaningful, message=FALSE, warning=FALSE, echo=FALSE, eval=TRUE, fig.height=9.5, fig.width=9.5}

tidy_bts_songs_meaningful_freq %>%
  ggplot(aes(x = proportion, y = proportion)) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 0.5) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(aes(color="FE769C"), alpha = 0.2, size = 2.5, width = 0.6, height = 0.6,
              show.legend = F) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  ggtitle("Meaningful English Words in All BTS's Albums")

```


Overall comparison amongst all the albums:
``` {r all_albums, message=FALSE, warning=FALSE, echo=FALSE, eval=TRUE, fig.height=9.5, fig.width=9.5}

tidy_bts_songs_meaningful_freq %>%
  ggplot(aes(x = proportion, y = proportion)) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 0.5) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(aes(color="FE769C"), alpha = 0.5, size = 2.5, width = 0.7, height = 0.7,
              show.legend = F) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  facet_wrap(~ album_title, nrow=2) +
  ggtitle("Comparison of All Album's Meaningful English Words")

```


The most common words amongst all albums:
``` {r eval=T, echo=F}
tidy_bts_songs_freq[order(-tidy_bts_songs_freq$n),]
```


The most common **_meaningful_** words amongst all albums:
``` {r eval=T, echo=F}
tidy_bts_songs_meaningful_freq[order(-tidy_bts_songs_meaningful_freq$n),]
```



Some words like 'love' and 'girl' weren't surprising to see amongst the top used lyric but others like 'bang' and 'yolo' really contrasted with that. This was my first webscraping project and I had lots of fun learning and analyzing the lyrics. I plan to analyze more lyrics in the future from BTS and other K-Pop girl groups and boy groups as well! 



